The Spatial and Temporal Domains of Modern Ecology

### 2017-12-18 paper/SI.tex
Revised supplemental figure titles, added in all figures and caption to SI. Updated gitignore to ignore all non RMd vignette components

The following text provides additional information on this study's Methods and Results.  The full manuscript, data, and code are available on an accompanying \href{https://github.com/ecohydro/ecoscales}{github repository}. \textbf{Note to editors and reviewers: this repository is currently private, but will be made public upon acceptance of manuscript. In the interim, the code and data can be downloaded from the following links}:
\href{https://www.dropbox.com/s/4r9h8mn1wa4kjsn/calibration.html?dl=0}{Calibration analysis}; \href{https://www.dropbox.com/s/n0zq5zufu96ktfl/calibration-set.xlsx?dl=0
}{Calibration dataset}; \href{https://www.dropbox.com/s/bzni8dhqy8un4fz/space-time.html?dl=0
}{Main analysis}; \href{https://www.dropbox.com/s/vujjo2x4f5kwqkb/main-results.xlsx?dl=0
}{Main dataset}

@@

   \Hitem \emph{\textbf{What is duration, and how do we estimate it?}} The duration is the total period of time over which the phenomenon of interest was observed. More specifically, in the case of repeated observations, this is the total time that elapsed between the first and last observations at a given point in space (or of the same individual organism or community). For once-off (unreplicated) observations, this time is equivalent to the sample duration. However, there may be cases where once-off observations may have a longer duration than the sample duration.  For example, consider a study that counts occurrences of pollinators over three years, using transects that are located in different locations within the broader study area during each year \cite{rollin_differences_2013-1}. The observations are therefore not strictly temporally replicated, but the authors control for year of collection in their subsequent analysis to avoid confounding effects.  In this case, we can consider the effective duration to be three years, as the temporal information is encoded in the analysis. 

@@

Fig. \ref{obshists} details the distributions of observations by method along the four primary dimensions, while Fig. \ref{obskde} reveals the densities of observations by method within the dimensional juxtapositions shown in Fig. 2 in the main text.

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{../vignettes/figures/fig1s.png}
\vspace{-20 pt}
\caption{Histograms of the resolution, extent, interval, and duration of observational scales, shown for all observational methods (top row) and for the four main observational methods (rows 2-5). Bars represent the average percentages for each bin realized after 1000 perturbed resamples, while grey bars indicate the 95\% confidence interval. Bar widths for interval and duration indicate differences in scale between x-axis labels. }
\label{obshists}
\end{figure}

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{../vignettes/figures/fig2s.png}
\vspace{-20 pt}
\caption{Kernel density estimates across all observational types (top row) and for each of the four primary observational types (rows 2-5). Density estimates for resolution (x axis) versus interval (y axis) are presented in the first column, duration (x) versus interval (y) in the second column, resolution (x) versus extent (y) in the third column, and duration (x) versus extent (y) in the fourth column. Density estimates were applied to the log-transformed values of each observational dimension, and were rescaled to represent percentages. The grey shaded areas represent physically impossible domains (e.g. intervals greater than duration).}
\label{obskde}
\end{figure}

@@

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{figures/stype_by_yr.png}
\vspace{10 pt}
\caption{Trends in percentage of observing methods by year of publication. The coefficient of a weighted (by number of studies in each year) linear regression fit to the annual percentages of observations made with remote sensing (left), field methods (center), and automated sensors (right) is presented at the top of each plot, as well as the regression coefficient of determination and p-value. }
\label{type_by_yr}
\end{figure}

\begin{figure}[ht]
%\begin{wrapfigure}{c}{1\textwidth}
\center{\includegraphics[width=0.8\textwidth]{figures/dim_by_yr.png}}
\vspace{5 pt}
\caption{Trends in observational scales by year of publication. The coefficient of a weighted (by number of studies in each year) linear regression, fit to the logarithm (base 10) of the mean scale values (calculated for each publication year) for the six assessed dimensions is presented at the top of each plot, as well as the model coefficient of determination and p-value. }
\label{sc_by_yr}
\end{figure}
%\clearpage

@@

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=0.9\textwidth]{../vignettes/figures/res_v_extent_ksize2.png}
\vspace{10 pt}
\caption{Two-dimensional kernel density estimates of observational densities within the domains defined by sampling interval and spatial resolution (left column) and duration and extent (right column), applied to log-transformed values of each observational dimension. Rows indicate the effects of selecting different bandwidths: 0.4 (top row); 0.7 (middle row); 1 (bottom row). }
\label{ksens}
\end{figure}

>>>>

The following text provides additional information on this study's Methods and Results.  The full manuscript, data, and code are available on an accompanying \href{https://github.com/agroimpacts/ecoscales}{github repository}. \textbf{Note to editors and reviewers: this repository is currently private, but will be made public upon acceptance of manuscript. In the interim, the entire project folder can be downloaded from the following \href{https://www.dropbox.com/sh/1l9em6p0wyabwr3/AADhCpFvqjv6y7VbL5tgB3Iqa?dl=0}{link}.}

@@

   \Hitem \emph{\textbf{What is duration, and how do we estimate it?}} The duration is the total period of time over which the phenomenon of interest was observed. More specifically, in the case of repeated observations, this is the total time that elapsed between the first and last observations at a given point in space (or of the same individual organism or community). For once-off (unreplicated) observations, this time is equivalent to the sample duration. However, there may be cases where once-off observations may have a longer duration than the sample duration.  For example, consider a study that counts occurrences of pollinators over three years, using transects that are located in different locations within the broader study area during each year \cite{rollin_differences_2013}. The observations are therefore not strictly temporally replicated, but the authors control for year of collection in their subsequent analysis to avoid confounding effects.  In this case, we can consider the effective duration to be three years, as the temporal information is encoded in the analysis. 

@@

Fig. \ref{obshists} details the distributions of observations by method along the four primary dimensions, while Fig. \ref{obskde} reveals the densities of observations by method within the dimensional juxtapositions shown in Fig. 2 in the main text. Fig. \ref{obsdiff} shows the how the differences between actual extent and extent  and actual duration and duration vary by observational type.

@@

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\textwidth]{../vignettes/figures/figS1.png}
\vspace{-20 pt}
\caption{Histograms of the resolution, extent, interval, and duration of observational scales, shown for all observational methods (top row) and for the four main observational methods (rows 2-5). Bars represent the average percentages for each bin realized after 1000 perturbed resamples, while grey bars indicate the 95\% confidence interval. Bar widths for interval and duration indicate differences in scale between x-axis labels. }
\label{obshists}
\end{figure}

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{../vignettes/figures/figS2.png}
\vspace{-20 pt}
\caption{Kernel density estimates across all observational methods (top row) and for each of the four primary observational methods (rows 2-5). Density estimates for resolution (x axis) versus interval (y axis) are presented in the first column, duration (x) versus interval (y) in the second column, resolution (x) versus extent (y) in the third column, and duration (x) versus extent (y) in the fourth column. Density estimates were applied to the log-transformed values of each observational dimension, and were rescaled to represent percentages. The grey shaded areas represent physically impossible domains (e.g. intervals greater than duration).}
\label{obskde}
\end{figure}

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\centering
\includegraphics[width=0.7\textwidth]{../vignettes/figures/figS3.png}
\vspace{-5 pt}
\caption{The difference between extent and \emph{actual} extent and duration and \emph{actual} duration, as calculated across all observational methods (top row) and for each of the four primary observational methods. Difference values are expressed in terms of how many orders of magnitude larger (or longer) extent (duration) is than actual extent (actual duration), and are summarized (as box plots, with circle in box representing the mean and line the median) in bins representing increasing scales of actual extent/duration.  The percentages of observations falling within each bin are indicated by the color of the inter-quartile and the numeric value above the upper whisker.}
\label{obsdiff}
\end{figure}

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=1\textwidth]{../vignettes/figures/figS4.png}
\vspace{10 pt}
\caption{Trends in percentage of observing methods by year of publication. The coefficient of a weighted (by number of studies in each year) linear regression fit to the annual percentages of observations made with remote sensing (left), field methods (center), and automated sensors (right) is presented at the top of each plot, as well as the regression coefficient of determination and p-value. }
\label{type_by_yr}
\end{figure}

\begin{figure}[ht]
%\begin{wrapfigure}{c}{1\textwidth}
\center{\includegraphics[width=0.8\textwidth]{../vignettes/figures/figS5.png}}
\vspace{5 pt}
\caption{Trends in observational scales by year of publication. The coefficient of a weighted (by number of studies in each year) linear regression, fit to the logarithm (base 10) of the mean scale values (calculated for each publication year) for the six assessed dimensions is presented at the top of each plot, as well as the model coefficient of determination and p-value. }
\label{sc_by_yr}
\end{figure}
%\clearpage

\begin{figure}[!ht]
%\begin{wrapfigure}{c}{1\textwidth}
\includegraphics[width=0.9\textwidth]{../vignettes/figures/figS6.png}
\vspace{10 pt}
\caption{Two-dimensional kernel density estimates of observational densities within the domains defined by sampling interval and spatial resolution (left column) and duration and extent (right column), applied to log-transformed values of each observational dimension. Rows indicate the effects of selecting different bandwidths: 0.4 (top row); 0.7 (middle row); 1 (bottom row). }
\label{ksens}
\end{figure}

### 2017-12-18 paper/main.tex
Revised supplemental figure titles, added in all figures and caption to SI. Updated gitignore to ignore all non RMd vignette components

This lower right to upper left orientation reflects the tradeoff between resolution and interval that is typical of satellite imaging \cite{estes_platform_2016}, and stands in contrast to the upper right to lower left line that stretches between this concentration and the high frequency (minute-hour intervals), high spatial resolution (0.1-100 cm$^2$) observations. This line demonstrates the opposite tradeoff that occurs with field-based observations, where larger plot sizes demand greater effort that in turn reduces sampling frequency \cite{kareiva_spatial_1988}.

>>>>

%This lower right to upper left orientation reflects the tradeoff between resolution and interval that is typical of satellite imaging \cite{estes_platform_2016}, and stands in contrast to the upper right to lower left line that stretches between this concentration and the high frequency (minute-hour intervals), high spatial resolution (0.1-100 cm$^2$) observations. This line demonstrates the opposite tradeoff that occurs with field-based observations, where larger plot sizes demand greater effort that in turn reduces sampling frequency \cite{kareiva_spatial_1988}.
